Doppler Imaging Fun

### 2019-06-13 tex/gitlinks.tex
woot

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a251a86a99ed85693dc35868dff23c6c4bdf40ed/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5fcbb15ba3e6d3c33496489dba346647c265f5d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-13 tex/ms.tex
woot

The equation for the observed disk-integrated spectrum is therefore
%
\begin{align}
    S(\xi) &= 
    \pi
    \mathcal{F}^{-1}
    \Big[
        \mathcal{F}(I_0)
        \,
        _{2}F_{1}
        \left(
            -\pi i k, \, 
            \frac{1}{2} - \pi i k; \,
            2; \,
            \beta_\mathrm{eq}^2
        \right)
    \Big]
\end{align}
%
Figure~\ref{fig:uniform}

\begin{figure}[p!]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/uniform.pdf}
    \oscaption{uniform}{%
        Hello.
        \label{fig:uniform}
    }
\end{figure}

>>>>

The equation for the observed disk-integrated spectrum is therefore
%
\begin{align}
    \label{eq:uniform}
    S(\xi) &= 
    \pi
    \mathcal{F}^{-1}
    \Big[
        \mathcal{F}(I_0)
        \,
        _{2}F_{1}
        \left(
            -\pi i k, \, 
            \frac{1}{2} - \pi i k; \,
            2; \,
            \beta_\mathrm{eq}^2
        \right)
    \Big]
\end{align}
%
Figure~\ref{fig:uniform} shows an example application of this equation
to the case of rotational broadening of a Gaussian absorption line.

\begin{figure}[p!]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/uniform.pdf}
    \oscaption{uniform}{%
        Application of Equation~(\ref{eq:uniform}) to computation
        of rotational line broadening of a Gaussian absorption line.
        \emph{Top:} A line centered at $\lambda = 1.00$ with 
        standard deviation $\sigma = 0.01$ (dashed black curve) is 
        redshifted by a Doppler parameter $\beta = 0.05$. The
        blue curve is the result obtained by interpolation, while
        the dashed orange curve is the result obtained by scaling
        the Fourier transform of the line according to
        Equation~(\ref{eq:translation}) and then applying the inverse
        Fourier transform.
        \emph{Bottom:} The same line profile is now integrated over
        the visible disk of a uniform, rigidly rotating star with
        $\beta_\mathrm{eq} = 0.05$ numerically (blue curve) and via
        the Fourier method (Equation~\ref{eq:uniform}). In both cases,
        the results agree to within the accuracy of the numerical
        approaches.
        \label{fig:uniform}
    }
\end{figure}
